Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-17 2017-EUROPAR/Gamification/paper.tex
Spelling checked
And caught quite a few... Phew!

One way of creating distributed computing system is to use volunteers who
provide their own computing resources or storage to contribute to a common effort.
By runnning a script in a web page, collaboration is straightforward, but also ephemeral.
Resources depend on the amount of time a user lends, whicn means that 
the user has to be kept engaged to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
NodIO with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment where a gammification technique is applied by adding a leaderboard 
showing the top scores achieved by registered contributors. In the NodIO system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation. 
The experiment results show that even if only a small percentege of users created an account,
those participating in the competition provided around 90\%.

@@

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger \& Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots for the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot\'s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands. This approach has been called {\em social cloud} \cite{6404452}, enphasizing the fact that user participation is gamified in order to obtain the most from it \cite{7027564}.

The proofs of concept described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems such as the one described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. Lately, researchers have tried to integrate volunteer as a part of a larger distributed computint effort \cite{leclerc2016seamless}. In fact, exclusive volunteer systems exhibit a certain amount of unpredictability and might be best used combined with available computing power.

@@

We made a call to participation on November 23th, 
2016 through the authors' social networks: ``Asking again for your help, we are conducting a computational experiment
that requires computer power. Can we borrow some of your CPU? just visit the web page (link)
and leave the tab open. Be part of the TOP TEN, register so we can track your participation.
The experiment will run until November 27th, Thanks!.'' We also included links to register and a deadline. Users visiting the pageafter the dealine were presented with a thank you message and a static leader board. 
%

>>>>

One way of creating distributed computing system is to use volunteers who
provide their own computing resources or storage to contribute to a common effort.
By running a script in a web page, collaboration is straightforward, but also ephemeral.
Resources depend on the amount of time a user lends, which means that 
the user has to be kept engaged to obtain as many computing cycles as
possible. In this paper, we analyze a volunteer-based evolutionary computing system called
NodIO with the objective of discovering rules that encourage volunteer
participation thus increasing the overall computing power. We present the results of
an experiment where a gamification technique is applied by adding a leader-board 
showing the top scores achieved by registered contributors. In the NodIO system volunteers can
participate without the need to create an account, so the question was
if the need to register would have a negative impact on user participation. 
The experiment results show that even if only a small percentage of users created an account,
those participating in the competition provided around 90\%.

@@

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger \& Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots for the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot\'s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands. This approach has been called {\em social cloud} \cite{6404452}, emphasizing the fact that user participation is gamified in order to obtain the most from it \cite{7027564}.

The proofs of concept described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems such as the one described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. Lately, researchers have tried to integrate volunteer as a part of a larger distributed computing effort \cite{leclerc2016seamless}. In fact, exclusive volunteer systems exhibit a certain amount of unpredictability and might be best used combined with available computing power.

@@

We made a call to participation on November 23th, 
2016 through the authors' social networks: ``Asking again for your help, we are conducting a computational experiment
that requires computer power. Can we borrow some of your CPU? just visit the web page (link)
and leave the tab open. Be part of the TOP TEN, register so we can track your participation.
The experiment will run until November 27th, Thanks!.'' We also included links to register and a deadline. Users visiting the page after the deadline were presented with a thank you message and a static leader board. 
%
